---
title: "script4_EnrichR_Treatment_TAPbyQNP"
author: "Shradha Mukherjee"
date: "Last updated January, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


1) This pipeline does a global miRNA target scan using enrichR as follows:
a) miRNAs target analysis (not just miR142 but other miRNAs too), using "TargetScan_microRNA_2017", "miRTarBase_2017", 
b) Gene ontology "GO_Biological_Process_2018". 
c) Pathway analysis "KEGG_2018"
d) Curated "OMIM_Disease", "OMIM_Expanded", all diseases 
e) Tissue type enrichment form human "Human_Gene_Atlas" and mouse "Mouse_Gene_Atlas", 
f) Potential drugs that can target the module genes "DrugMatrix" and "DSigDB" .
g) Transcription factor regulation "ChEA 2016" and "ENCODE TF ChIP-seq 2015"
h) Epigenetic regulation "Epigenomics Roadmap HM ChIP-seq" and "ENCODE Histone Modifications 2015"
i) cancer cell lines "Cancer Cell Line Encyclopedia" and "NCI-60 Cancer Cell Lines"

2)To use this code for different DEG list of genes change the genes in mygenes


Select color module of interest
###Step24: Load libraries and save working directory
```{r}
library(WGCNA)
library(ggmap)#plots
library(gplots)#plots
library(RColorBrewer)#color pallet
library(Hmisc)#for corelation plot
library(enrichR)#GO analysis and pathway analysis
library(dplyr)
library(plyr)
library(qpcR)
options(stringsAsFactors = FALSE)
```

```{r}
wd<-getwd()
```

###Step25: Import test dataset
#Import the test dataset (your new dataset) with genes 
```{r}
#Import new DEG data we got from our analysis containing genes
load(file="./DEG_AllDEGmethods_results/DEG_AllDEGmethodsnames.RData")
#DEG_AllDEGmethodsnames=as.data.frame(DEG_AllDEGmethodsnames)
```

```{r}
mygenes=c(DEG_AllDEGmethodsnames[,1],DEG_AllDEGmethodsnames[,2], DEG_AllDEGmethodsnames[,3],DEG_AllDEGmethodsnames[,4])
mygenes=as.data.frame(mygenes)
mygenes$Category="TAPbyQNP"
colnames(mygenes)=c("Gene", "Category")
mygenes=mygenes[!duplicated(mygenes$Gene),]
dim(mygenes)
head(mygenes)
```

```{r}
#Export for use in WGCNA enrichment test
write.csv(mygenes, "ForWGCNA_DEGup_TAPbyQNP.csv")
```

###########################################################################################Comparison with enrichR database STARTs here#########################################################################################

###Step26: Get enrichR databases of interest and perform enrichment analysis
```{r}
dbs <- listEnrichrDbs()
dbs
```

```{r}
#select GO process and KEGG pathway of choice
dbs_select<-c("GO_Biological_Process_2018", "KEGG_2016", "TargetScan_microRNA_2017", "miRTarBase_2017", "OMIM_Disease", "OMIM_Expanded", "Human_Gene_Atlas", "Mouse_Gene_Atlas", "DrugMatrix", "DSigDB","Epigenomics_Roadmap_HM_ChIP-seq", "ENCODE_and_ChEA_Consensus_TFs_from_ChIP-X")
dbs_select
```

```{r}
#compare our genes from TAPbyQNP to selected GO process and KEGG pathway
enriched <- enrichr(mygenes$Gene, dbs_select)
```

###########################################################################################GO analysis############################################################################################################

###Step27: GO Biological Process results

```{r}
#Export GO Biological Process result
my_genes_GO_BP<-as.data.frame(enriched[["GO_Biological_Process_2018"]])
my_genes_GO_BP_sig0.05<-my_genes_GO_BP[my_genes_GO_BP$Adjusted.P.value <0.05,]
head(my_genes_GO_BP_sig0.05)
head(my_genes_GO_BP)
```

```{r}
#Creating a new column with number of genes that overlapped
my_genes_GO_BP_sig0.05_new<-my_genes_GO_BP_sig0.05

my_genes_GO_BP_sig0.05_new$Overlap_Number<-my_genes_GO_BP_sig0.05$Overlap

my_genes_GO_BP_sig0.05_new$Overlap_Number<-gsub("/.*","",my_genes_GO_BP_sig0.05_new$Overlap_Number)

my_genes_GO_BP_sig0.05_new$Overlap_Number<-as.integer(my_genes_GO_BP_sig0.05_new$Overlap_Number)

write.csv(my_genes_GO_BP_sig0.05_new,file="Step27_result_GO_Biological_Process_2018_sig0.05_TAPbyQNP.csv")
```

```{r}
# Basic barplot
folder=getwd()
pdf(paste0("Step27_plot_Sig0.05-GO_Biological_Process_plot_", "TAPbyQNP",".pdf"), height=10, width=5)
p1<-ggplot(data=my_genes_GO_BP_sig0.05_new, aes(x=Term, y=Overlap_Number, fill=Adjusted.P.value))+
  geom_bar(position="stack", stat="identity")+
  labs(title=paste0(folder,"_","GO_Biological_Process_Comparison"))+
  labs(x="Module names")+
  theme(axis.text.x=element_text(angle=90,hjust=1)) +
  labs(y="Number of genes overlap")+
  labs(caption="based on enrichR database")+
  scale_fill_gradient(low="black",high="red")
  #theme(plot.margin = margin(2,2,2,2, "cm"), plot.background = element_rect(fill = "white"))
print(p1)
dev.off()
```

```{r}
#Creating a new column with number of genes that overlapped
my_genes_GO_BP_new<-my_genes_GO_BP

my_genes_GO_BP_new$Overlap_Number<-my_genes_GO_BP$Overlap

my_genes_GO_BP_new$Overlap_Number<-gsub("/.*","",my_genes_GO_BP_new$Overlap_Number)

my_genes_GO_BP_new$Overlap_Number<-as.integer(my_genes_GO_BP_new$Overlap_Number)

write.csv(my_genes_GO_BP_new,file="Step27_result_GO_Biological_Process_2018_TAPbyQNP.csv")
```

```{r}
# Basic barplot
folder=getwd()
pdf(paste0("Step27_plot_GO_Biological_Process_plot_", "TAPbyQNP",".pdf"), height=10, width=5)
p2<-ggplot(data=my_genes_GO_BP_new, aes(x=Term, y=Overlap_Number, fill=Adjusted.P.value))+
  geom_bar(position="stack", stat="identity")+
  labs(title=paste0(folder,"_","GO_Biological_Process_Comparison"))+
  labs(x="Module names")+
  theme(axis.text.x=element_text(angle=90,hjust=1)) +
  labs(y="Number of genes overlap")+
  labs(caption="based on enrichR database")+
  scale_fill_gradient(low="black",high="red")
  #theme(plot.margin = margin(2,2,2,2, "cm"), plot.background = element_rect(fill = "white"))
print(p2)
dev.off()
```

###########################################################################################KEEG pathway analysis############################################################################################################

###Step28: KEGG pathway results

```{r}
#Export KEGG pathway result
my_genes_KEGG<-as.data.frame(enriched[["KEGG_2016"]])
my_genes_KEGG_sig0.05<-my_genes_KEGG[my_genes_KEGG$Adjusted.P.value <0.05,]
head(my_genes_KEGG_sig0.05)
head(my_genes_KEGG)
```

```{r}
#Creating a new column with number of genes that overlapped
my_genes_KEGG_sig0.05_new<-my_genes_KEGG_sig0.05

my_genes_KEGG_sig0.05_new$Overlap_Number<-my_genes_KEGG_sig0.05$Overlap

my_genes_KEGG_sig0.05_new$Overlap_Number<-gsub("/.*","",my_genes_KEGG_sig0.05_new$Overlap_Number)

my_genes_KEGG_sig0.05_new$Overlap_Number<-as.integer(my_genes_KEGG_sig0.05_new$Overlap_Number)

write.csv(my_genes_KEGG_sig0.05_new,file="Step28_result_KEGG_Pathway_2016_sig0.05_TAPbyQNP.csv")
```

```{r}
# Basic barplot
folder=getwd()
pdf(paste0("Step28_plot_Sig0.05-KEGG_Pathway_plot_", "TAPbyQNP",".pdf"), height=10, width=5)
p3<-ggplot(data=my_genes_KEGG_sig0.05_new, aes(x=Term, y=Overlap_Number, fill=Adjusted.P.value))+
  geom_bar(position="stack", stat="identity")+
  labs(title=paste0(folder,"_","KEGG_Pathway_Comparison"))+
  labs(x="Module names")+
  theme(axis.text.x=element_text(angle=90,hjust=1)) +
  labs(y="Number of genes overlap")+
  labs(caption="based on enrichR database")+
  scale_fill_gradient(low="black",high="red")
  #theme(plot.margin = margin(2,2,2,2, "cm"), plot.background = element_rect(fill = "white"))
print(p3)
dev.off()
```

```{r}
#Creating a new column with number of genes that overlapped
my_genes_KEGG_new<-my_genes_KEGG

my_genes_KEGG_new$Overlap_Number<-my_genes_KEGG$Overlap

my_genes_KEGG_new$Overlap_Number<-gsub("/.*","",my_genes_KEGG_new$Overlap_Number)

my_genes_KEGG_new$Overlap_Number<-as.integer(my_genes_KEGG_new$Overlap_Number)

write.csv(my_genes_KEGG_new,file="Step28_result_KEGG_Pathway_2016_TAPbyQNP.csv")
```

```{r}
# Basic barplot
folder=getwd()
pdf(paste0("Step28_plot_KEGG_Pathway_plot_", "TAPbyQNP",".pdf"), height=10, width=5)
p4<-ggplot(data=my_genes_KEGG_new, aes(x=Term, y=Overlap_Number, fill=Adjusted.P.value))+
  geom_bar(position="stack", stat="identity")+
  labs(title=paste0(folder,"_","KEGG_Pathway_Comparison"))+
  labs(x="Module names")+
  theme(axis.text.x=element_text(angle=90,hjust=1)) +
  labs(y="Number of genes overlap")+
  labs(caption="based on enrichR database")+
  scale_fill_gradient(low="black",high="red")
  #theme(plot.margin = margin(2,2,2,2, "cm"), plot.background = element_rect(fill = "white"))
print(p4)
dev.off()
```

###########################################################################################TargetScan base analysis############################################################################################################

###Step29: TargetScan target genes analysis results

```{r}
#Export TargetScan pathway result
my_genes_TargetScan<-as.data.frame(enriched[["TargetScan_microRNA_2017"]])
my_genes_TargetScan_sig0.05<-my_genes_TargetScan[my_genes_TargetScan$Adjusted.P.value <0.05,]
head(my_genes_TargetScan_sig0.05)
head(my_genes_TargetScan)
```

```{r}
#Creating a new column with number of genes that overlapped
my_genes_TargetScan_sig0.05_new<-my_genes_TargetScan_sig0.05

my_genes_TargetScan_sig0.05_new$Overlap_Number<-my_genes_TargetScan_sig0.05$Overlap

my_genes_TargetScan_sig0.05_new$Overlap_Number<-gsub("/.*","",my_genes_TargetScan_sig0.05_new$Overlap_Number)

my_genes_TargetScan_sig0.05_new$Overlap_Number<-as.integer(my_genes_TargetScan_sig0.05_new$Overlap_Number)

write.csv(my_genes_TargetScan_sig0.05_new,file="Step29_result_TargetScan_microRNA_2017_sig0.05_TAPbyQNP.csv")
```

```{r}
# Basic barplot
folder=getwd()
pdf(paste0("Step29_plot_sig0.05-TargetScan_Pathway_plot_", "TAPbyQNP",".pdf"), height=10, width=5)
p5<-ggplot(data=my_genes_TargetScan_sig0.05_new, aes(x=Term, y=Overlap_Number, fill=Adjusted.P.value))+
  geom_bar(position="stack", stat="identity")+
  labs(title=paste0(folder,"_","TargetScan_Gene_Targets_Comparison"))+
  labs(x="Module names")+
  theme(axis.text.x=element_text(angle=90,hjust=1)) +
  labs(y="Number of genes overlap")+
  labs(caption="based on data from enrichR")+
  scale_fill_gradient(low="black",high="red")
  #theme(plot.margin = margin(2,2,2,2, "cm"), plot.background = element_rect(fill = "white"))
print(p5)
dev.off()
```

```{r}
#Creating a new column with number of genes that overlapped
my_genes_TargetScan_new<-my_genes_TargetScan

my_genes_TargetScan_new$Overlap_Number<-my_genes_TargetScan$Overlap

my_genes_TargetScan_new$Overlap_Number<-gsub("/.*","",my_genes_TargetScan_new$Overlap_Number)

my_genes_TargetScan_new$Overlap_Number<-as.integer(my_genes_TargetScan_new$Overlap_Number)

write.csv(my_genes_TargetScan_new,file="Step29_result_TargetScan_microRNA_2017_TAPbyQNP.csv")
```

```{r}
# Basic barplot
folder=getwd()
pdf(paste0("Step29_plot_TargetScan_Pathway_plot_", "TAPbyQNP",".pdf"), height=10, width=5)
p6<-ggplot(data=my_genes_TargetScan_new, aes(x=Term, y=Overlap_Number, fill=Adjusted.P.value))+
  geom_bar(position="stack", stat="identity")+
  labs(title=paste0(folder,"_","TargetScan_Gene_Targets_Comparison"))+
  labs(x="Module names")+
  theme(axis.text.x=element_text(angle=90,hjust=1)) +
  labs(y="Number of genes overlap")+
  labs(caption="based on data from enrichR")+
  scale_fill_gradient(low="black",high="red")
  #theme(plot.margin = margin(2,2,2,2, "cm"), plot.background = element_rect(fill = "white"))
print(p6)
dev.off()
```

###########################################################################################miRTarBase base analysis############################################################################################################

###Step30: miRTarBase target genes analysis results

```{r}
#Export miRTarBase pathway result
my_genes_miRTarBase<-as.data.frame(enriched[["miRTarBase_2017"]])
my_genes_miRTarBase_sig0.05<-my_genes_miRTarBase[my_genes_miRTarBase$Adjusted.P.value <0.05,]
head(my_genes_miRTarBase_sig0.05)
head(my_genes_miRTarBase)
```

```{r}
#Creating a new column with number of genes that overlapped
my_genes_miRTarBase_sig0.05_new<-my_genes_miRTarBase_sig0.05

my_genes_miRTarBase_sig0.05_new$Overlap_Number<-my_genes_miRTarBase_sig0.05$Overlap

my_genes_miRTarBase_sig0.05_new$Overlap_Number<-gsub("/.*","",my_genes_miRTarBase_sig0.05_new$Overlap_Number)

my_genes_miRTarBase_sig0.05_new$Overlap_Number<-as.integer(my_genes_miRTarBase_sig0.05_new$Overlap_Number)

write.csv(my_genes_miRTarBase_sig0.05_new,file="Step30_result_miRTarBase_2017_sig0.05_TAPbyQNP.csv")
```

```{r}
# Basic barplot
folder=getwd()
pdf(paste0("Step30_plot_sig0.05-miRTarBase_Pathway_plot_", "TAPbyQNP",".pdf"), height=10, width=5)
p7<-ggplot(data=my_genes_miRTarBase_sig0.05_new, aes(x=Term, y=Overlap_Number, fill=Adjusted.P.value))+
  geom_bar(position="stack", stat="identity")+
  labs(title=paste0(folder,"_","miRTarBase_Gene_Targets_Comparison"))+
  labs(x="Module names")+
  theme(axis.text.x=element_text(angle=90,hjust=1)) +
  labs(y="Number of genes overlap")+
  labs(caption="based on data from enrichR")+
  scale_fill_gradient(low="black",high="red")
  #theme(plot.margin = margin(2,2,2,2, "cm"), plot.background = element_rect(fill = "white"))
print(p7)
dev.off()
```

```{r}
#Creating a new column with number of genes that overlapped
my_genes_miRTarBase_new<-my_genes_miRTarBase

my_genes_miRTarBase_new$Overlap_Number<-my_genes_miRTarBase$Overlap

my_genes_miRTarBase_new$Overlap_Number<-gsub("/.*","",my_genes_miRTarBase_new$Overlap_Number)

my_genes_miRTarBase_new$Overlap_Number<-as.integer(my_genes_miRTarBase_new$Overlap_Number)

write.csv(my_genes_miRTarBase_new,file="Step30_result_miRTarBase_2017_TAPbyQNP.csv")
```

```{r}
# Basic barplot
folder=getwd()
pdf(paste0("Step30_plot_miRTarBase_Pathway_plot_", "TAPbyQNP",".pdf"), height=10, width=5)
p8<-ggplot(data=my_genes_miRTarBase_new, aes(x=Term, y=Overlap_Number, fill=Adjusted.P.value))+
  geom_bar(position="stack", stat="identity")+
  labs(title=paste0(folder,"_","miRTarBase_Gene_Targets_Comparison"))+
  labs(x="Module names")+
  theme(axis.text.x=element_text(angle=90,hjust=1)) +
  labs(y="Number of genes overlap")+
  labs(caption="based on data from enrichR")+
  scale_fill_gradient(low="black",high="red")
  #theme(plot.margin = margin(2,2,2,2, "cm"), plot.background = element_rect(fill = "white"))
print(p8)
dev.off()
```

###########################################################################################OMIM_Disease base analysis############################################################################################################

###Step31: OMIM_Disease target genes analysis results

```{r}
#Export OMIM_Disease pathway result
my_genes_OMIM_Disease<-as.data.frame(enriched[["OMIM_Disease"]])
my_genes_OMIM_Disease_sig0.05<-my_genes_OMIM_Disease[my_genes_OMIM_Disease$Adjusted.P.value <0.05,]
head(my_genes_OMIM_Disease_sig0.05)
head(my_genes_OMIM_Disease)
```

```{r}
#Creating a new column with number of genes that overlapped
my_genes_OMIM_Disease_sig0.05_new<-my_genes_OMIM_Disease_sig0.05

my_genes_OMIM_Disease_sig0.05_new$Overlap_Number<-my_genes_OMIM_Disease_sig0.05$Overlap

my_genes_OMIM_Disease_sig0.05_new$Overlap_Number<-gsub("/.*","",my_genes_OMIM_Disease_sig0.05_new$Overlap_Number)

my_genes_OMIM_Disease_sig0.05_new$Overlap_Number<-as.integer(my_genes_OMIM_Disease_sig0.05_new$Overlap_Number)

write.csv(my_genes_OMIM_Disease_sig0.05_new,file="Step31_result_OMIM_Disease_sig0.05_TAPbyQNP.csv")
```

```{r}
# Basic barplot
folder=getwd()
pdf(paste0("Step31_plot_sig0.05-OMIM_Disease_Pathway_plot_", "TAPbyQNP",".pdf"), height=10, width=5)
p9<-ggplot(data=my_genes_OMIM_Disease_sig0.05_new, aes(x=Term, y=Overlap_Number, fill=Adjusted.P.value))+
  geom_bar(position="stack", stat="identity")+
  labs(title=paste0(folder,"_","OMIM_Disease_Gene_Targets_Comparison"))+
  labs(x="Module names")+
  theme(axis.text.x=element_text(angle=90,hjust=1)) +
  labs(y="Number of genes overlap")+
  labs(caption="based on data from enrichR")+
  scale_fill_gradient(low="black",high="red")
  #theme(plot.margin = margin(2,2,2,2, "cm"), plot.background = element_rect(fill = "white"))
print(p9)
dev.off()
```

```{r}
#Creating a new column with number of genes that overlapped
my_genes_OMIM_Disease_new<-my_genes_OMIM_Disease

my_genes_OMIM_Disease_new$Overlap_Number<-my_genes_OMIM_Disease$Overlap

my_genes_OMIM_Disease_new$Overlap_Number<-gsub("/.*","",my_genes_OMIM_Disease_new$Overlap_Number)

my_genes_OMIM_Disease_new$Overlap_Number<-as.integer(my_genes_OMIM_Disease_new$Overlap_Number)

write.csv(my_genes_OMIM_Disease_new,file="Step31_result_OMIM_Disease_TAPbyQNP.csv")
```

```{r}
# Basic barplot
folder=getwd()
pdf(paste0("Step31_plot_OMIM_Disease_Pathway_plot_", "TAPbyQNP",".pdf"), height=10, width=5)
p10<-ggplot(data=my_genes_OMIM_Disease_new, aes(x=Term, y=Overlap_Number, fill=Adjusted.P.value))+
  geom_bar(position="stack", stat="identity")+
  labs(title=paste0(folder,"_","OMIM_Disease_Gene_Targets_Comparison"))+
  labs(x="Module names")+
  theme(axis.text.x=element_text(angle=90,hjust=1)) +
  labs(y="Number of genes overlap")+
  labs(caption="based on data from enrichR")+
  scale_fill_gradient(low="black",high="red")
  #theme(plot.margin = margin(2,2,2,2, "cm"), plot.background = element_rect(fill = "white"))
print(p10)
dev.off()
```

###########################################################################################OMIM_Expanded base analysis############################################################################################################

###Step32: OMIM_Expanded target genes analysis results

```{r}
#Export OMIM_Expanded pathway result
my_genes_OMIM_Expanded<-as.data.frame(enriched[["OMIM_Expanded"]])
my_genes_OMIM_Expanded_sig0.05<-my_genes_OMIM_Expanded[my_genes_OMIM_Expanded$Adjusted.P.value <0.05,]
head(my_genes_OMIM_Expanded_sig0.05)
head(my_genes_OMIM_Expanded)
```

```{r}
#Creating a new column with number of genes that overlapped
my_genes_OMIM_Expanded_sig0.05_new<-my_genes_OMIM_Expanded_sig0.05

my_genes_OMIM_Expanded_sig0.05_new$Overlap_Number<-my_genes_OMIM_Expanded_sig0.05$Overlap

my_genes_OMIM_Expanded_sig0.05_new$Overlap_Number<-gsub("/.*","",my_genes_OMIM_Expanded_sig0.05_new$Overlap_Number)

my_genes_OMIM_Expanded_sig0.05_new$Overlap_Number<-as.integer(my_genes_OMIM_Expanded_sig0.05_new$Overlap_Number)

write.csv(my_genes_OMIM_Expanded_sig0.05_new,file="Step32_result_OMIM_Expanded_sig0.05_TAPbyQNP.csv")
```

```{r}
# Basic barplot
folder=getwd()
pdf(paste0("Step32_plot_sig0.05-OMIM_Expanded_Pathway_plot_", "TAPbyQNP",".pdf"), height=10, width=5)
p11<-ggplot(data=my_genes_OMIM_Expanded_sig0.05_new, aes(x=Term, y=Overlap_Number, fill=Adjusted.P.value))+
  geom_bar(position="stack", stat="identity")+
  labs(title=paste0(folder,"_","OMIM_Expanded_Gene_Targets_Comparison"))+
  labs(x="Module names")+
  theme(axis.text.x=element_text(angle=90,hjust=1)) +
  labs(y="Number of genes overlap")+
  labs(caption="based on data from enrichR")+
  scale_fill_gradient(low="black",high="red")
  #theme(plot.margin = margin(2,2,2,2, "cm"), plot.background = element_rect(fill = "white"))
print(p11)
dev.off()
```

```{r}
#Creating a new column with number of genes that overlapped
my_genes_OMIM_Expanded_new<-my_genes_OMIM_Expanded

my_genes_OMIM_Expanded_new$Overlap_Number<-my_genes_OMIM_Expanded$Overlap

my_genes_OMIM_Expanded_new$Overlap_Number<-gsub("/.*","",my_genes_OMIM_Expanded_new$Overlap_Number)

my_genes_OMIM_Expanded_new$Overlap_Number<-as.integer(my_genes_OMIM_Expanded_new$Overlap_Number)

write.csv(my_genes_OMIM_Expanded_new,file="Step32_result_OMIM_Expanded_TAPbyQNP.csv")
```

```{r}
# Basic barplot
folder=getwd()
pdf(paste0("Step32_plot_OMIM_Expanded_Pathway_plot_", "TAPbyQNP",".pdf"), height=10, width=5)
p12<-ggplot(data=my_genes_OMIM_Expanded_new, aes(x=Term, y=Overlap_Number, fill=Adjusted.P.value))+
  geom_bar(position="stack", stat="identity")+
  labs(title=paste0(folder,"_","OMIM_Expanded_Gene_Targets_Comparison"))+
  labs(x="Module names")+
  theme(axis.text.x=element_text(angle=90,hjust=1)) +
  labs(y="Number of genes overlap")+
  labs(caption="based on data from enrichR")+
  scale_fill_gradient(low="black",high="red")
  #theme(plot.margin = margin(2,2,2,2, "cm"), plot.background = element_rect(fill = "white"))
print(p12)
dev.off()
```

###########################################################################################Human_Gene_Atlas base analysis############################################################################################################

###Step33: Human_Gene_Atlas target genes analysis results

```{r}
#Export Human_Gene_Atlas pathway result
my_genes_Human_Gene_Atlas<-as.data.frame(enriched[["Human_Gene_Atlas"]])
my_genes_Human_Gene_Atlas_sig0.05<-my_genes_Human_Gene_Atlas[my_genes_Human_Gene_Atlas$Adjusted.P.value <0.05,]
head(my_genes_Human_Gene_Atlas_sig0.05)
head(my_genes_Human_Gene_Atlas)
```

```{r}
#Creating a new column with number of genes that overlapped
my_genes_Human_Gene_Atlas_sig0.05_new<-my_genes_Human_Gene_Atlas_sig0.05

my_genes_Human_Gene_Atlas_sig0.05_new$Overlap_Number<-my_genes_Human_Gene_Atlas_sig0.05$Overlap

my_genes_Human_Gene_Atlas_sig0.05_new$Overlap_Number<-gsub("/.*","",my_genes_Human_Gene_Atlas_sig0.05_new$Overlap_Number)

my_genes_Human_Gene_Atlas_sig0.05_new$Overlap_Number<-as.integer(my_genes_Human_Gene_Atlas_sig0.05_new$Overlap_Number)

write.csv(my_genes_Human_Gene_Atlas_sig0.05_new,file="Step33_result_Human_Gene_Atlas_sig0.05_TAPbyQNP.csv")
```

```{r}
# Basic barplot
folder=getwd()
pdf(paste0("Step33_plot_sig0.05-Human_Gene_Atlas_Pathway_plot_", "TAPbyQNP",".pdf"), height=10, width=5)
p13<-ggplot(data=my_genes_Human_Gene_Atlas_sig0.05_new, aes(x=Term, y=Overlap_Number, fill=Adjusted.P.value))+
  geom_bar(position="stack", stat="identity")+
  labs(title=paste0(folder,"_","Human_Gene_Atlas_Gene_Targets_Comparison"))+
  labs(x="Module names")+
  theme(axis.text.x=element_text(angle=90,hjust=1)) +
  labs(y="Number of genes overlap")+
  labs(caption="based on data from enrichR")+
  scale_fill_gradient(low="black",high="red")
  #theme(plot.margin = margin(2,2,2,2, "cm"), plot.background = element_rect(fill = "white"))
print(p13)
dev.off()
```

```{r}
#Creating a new column with number of genes that overlapped
my_genes_Human_Gene_Atlas_new<-my_genes_Human_Gene_Atlas

my_genes_Human_Gene_Atlas_new$Overlap_Number<-my_genes_Human_Gene_Atlas$Overlap

my_genes_Human_Gene_Atlas_new$Overlap_Number<-gsub("/.*","",my_genes_Human_Gene_Atlas_new$Overlap_Number)

my_genes_Human_Gene_Atlas_new$Overlap_Number<-as.integer(my_genes_Human_Gene_Atlas_new$Overlap_Number)

write.csv(my_genes_Human_Gene_Atlas_new,file="Step33_result_Human_Gene_Atlas_TAPbyQNP.csv")
```

```{r}
# Basic barplot
folder=getwd()
pdf(paste0("Step33_plot_Human_Gene_Atlas_Pathway_plot_", "TAPbyQNP",".pdf"), height=10, width=5)
p14<-ggplot(data=my_genes_Human_Gene_Atlas_new, aes(x=Term, y=Overlap_Number, fill=Adjusted.P.value))+
  geom_bar(position="stack", stat="identity")+
  labs(title=paste0(folder,"_","Human_Gene_Atlas_Gene_Targets_Comparison"))+
  labs(x="Module names")+
  theme(axis.text.x=element_text(angle=90,hjust=1)) +
  labs(y="Number of genes overlap")+
  labs(caption="based on data from enrichR")+
  scale_fill_gradient(low="black",high="red")
  #theme(plot.margin = margin(2,2,2,2, "cm"), plot.background = element_rect(fill = "white"))
print(p14)
dev.off()
```

###########################################################################################Mouse_Gene_Atlas base analysis############################################################################################################

###Step34: Mouse_Gene_Atlas target genes analysis results

```{r}
#Export Mouse_Gene_Atlas pathway result
my_genes_Mouse_Gene_Atlas<-as.data.frame(enriched[["Mouse_Gene_Atlas"]])
my_genes_Mouse_Gene_Atlas_sig0.05<-my_genes_Mouse_Gene_Atlas[my_genes_Mouse_Gene_Atlas$Adjusted.P.value <0.05,]
head(my_genes_Mouse_Gene_Atlas_sig0.05)
head(my_genes_Mouse_Gene_Atlas)
```

```{r}
#Creating a new column with number of genes that overlapped
my_genes_Mouse_Gene_Atlas_sig0.05_new<-my_genes_Mouse_Gene_Atlas_sig0.05

my_genes_Mouse_Gene_Atlas_sig0.05_new$Overlap_Number<-my_genes_Mouse_Gene_Atlas_sig0.05$Overlap

my_genes_Mouse_Gene_Atlas_sig0.05_new$Overlap_Number<-gsub("/.*","",my_genes_Mouse_Gene_Atlas_sig0.05_new$Overlap_Number)

my_genes_Mouse_Gene_Atlas_sig0.05_new$Overlap_Number<-as.integer(my_genes_Mouse_Gene_Atlas_sig0.05_new$Overlap_Number)

write.csv(my_genes_Mouse_Gene_Atlas_sig0.05_new,file="Step34_result_Mouse_Gene_Atlas_sig0.05_TAPbyQNP.csv")
```

```{r}
# Basic barplot
folder=getwd()
pdf(paste0("Step34_plot_sig0.05-Mouse_Gene_Atlas_Pathway_plot_", "TAPbyQNP",".pdf"), height=10, width=5)
p15<-ggplot(data=my_genes_Mouse_Gene_Atlas_sig0.05_new, aes(x=Term, y=Overlap_Number, fill=Adjusted.P.value))+
  geom_bar(position="stack", stat="identity")+
  labs(title=paste0(folder,"_","Mouse_Gene_Atlas_Gene_Targets_Comparison"))+
  labs(x="Module names")+
  theme(axis.text.x=element_text(angle=90,hjust=1)) +
  labs(y="Number of genes overlap")+
  labs(caption="based on data from enrichR")+
  scale_fill_gradient(low="black",high="red")
  #theme(plot.margin = margin(2,2,2,2, "cm"), plot.background = element_rect(fill = "white"))
print(p15)
dev.off()
```

```{r}
#Creating a new column with number of genes that overlapped
my_genes_Mouse_Gene_Atlas_new<-my_genes_Mouse_Gene_Atlas

my_genes_Mouse_Gene_Atlas_new$Overlap_Number<-my_genes_Mouse_Gene_Atlas$Overlap

my_genes_Mouse_Gene_Atlas_new$Overlap_Number<-gsub("/.*","",my_genes_Mouse_Gene_Atlas_new$Overlap_Number)

my_genes_Mouse_Gene_Atlas_new$Overlap_Number<-as.integer(my_genes_Mouse_Gene_Atlas_new$Overlap_Number)

write.csv(my_genes_Mouse_Gene_Atlas_new,file="Step34_result_Mouse_Gene_Atlas_TAPbyQNP.csv")
```

```{r}
# Basic barplot
folder=getwd()
pdf(paste0("Step34_plot_Mouse_Gene_Atlas_Pathway_plot_", "TAPbyQNP",".pdf"), height=10, width=5)
p16<-ggplot(data=my_genes_Mouse_Gene_Atlas_new, aes(x=Term, y=Overlap_Number, fill=Adjusted.P.value))+
  geom_bar(position="stack", stat="identity")+
  labs(title=paste0(folder,"_","Mouse_Gene_Atlas_Gene_Targets_Comparison"))+
  labs(x="Module names")+
  theme(axis.text.x=element_text(angle=90,hjust=1)) +
  labs(y="Number of genes overlap")+
  labs(caption="based on data from enrichR")+
  scale_fill_gradient(low="black",high="red")
  #theme(plot.margin = margin(2,2,2,2, "cm"), plot.background = element_rect(fill = "white"))
print(p16)
dev.off()
```

###########################################################################################DrugMatrix base analysis############################################################################################################

###Step35: DrugMatrix target genes analysis results

```{r}
#Export DrugMatrix pathway result
my_genes_DrugMatrix<-as.data.frame(enriched[["DrugMatrix"]])
my_genes_DrugMatrix_sig0.05<-my_genes_DrugMatrix[my_genes_DrugMatrix$Adjusted.P.value <0.05,]
head(my_genes_DrugMatrix_sig0.05)
head(my_genes_DrugMatrix)
```

```{r}
#Creating a new column with number of genes that overlapped
my_genes_DrugMatrix_sig0.05_new<-my_genes_DrugMatrix_sig0.05

my_genes_DrugMatrix_sig0.05_new$Overlap_Number<-my_genes_DrugMatrix_sig0.05$Overlap

my_genes_DrugMatrix_sig0.05_new$Overlap_Number<-gsub("/.*","",my_genes_DrugMatrix_sig0.05_new$Overlap_Number)

my_genes_DrugMatrix_sig0.05_new$Overlap_Number<-as.integer(my_genes_DrugMatrix_sig0.05_new$Overlap_Number)

write.csv(my_genes_DrugMatrix_sig0.05_new,file="Step35_result_DrugMatrix_sig0.05_TAPbyQNP.csv")
```

```{r}
# Basic barplot
folder=getwd()
pdf(paste0("Step35_plot_sig0.05-DrugMatrix_Pathway_plot_", "TAPbyQNP",".pdf"), height=10, width=5)
p17<-ggplot(data=my_genes_DrugMatrix_sig0.05_new, aes(x=Term, y=Overlap_Number, fill=Adjusted.P.value))+
  geom_bar(position="stack", stat="identity")+
  labs(title=paste0(folder,"_","DrugMatrix_Gene_Targets_Comparison"))+
  labs(x="Module names")+
  theme(axis.text.x=element_text(angle=90,hjust=1)) +
  labs(y="Number of genes overlap")+
  labs(caption="based on data from enrichR")+
  scale_fill_gradient(low="black",high="red")
  #theme(plot.margin = margin(2,2,2,2, "cm"), plot.background = element_rect(fill = "white"))
print(p17)
dev.off()
```

```{r}
#Creating a new column with number of genes that overlapped
my_genes_DrugMatrix_new<-my_genes_DrugMatrix

my_genes_DrugMatrix_new$Overlap_Number<-my_genes_DrugMatrix$Overlap

my_genes_DrugMatrix_new$Overlap_Number<-gsub("/.*","",my_genes_DrugMatrix_new$Overlap_Number)

my_genes_DrugMatrix_new$Overlap_Number<-as.integer(my_genes_DrugMatrix_new$Overlap_Number)

write.csv(my_genes_DrugMatrix_new,file="Step35_result_DrugMatrix_TAPbyQNP.csv")
```

```{r}
# Basic barplot
folder=getwd()
pdf(paste0("Step35_plot_DrugMatrix_Pathway_plot_", "TAPbyQNP",".pdf"), height=10, width=5)
p18<-ggplot(data=my_genes_DrugMatrix_new, aes(x=Term, y=Overlap_Number, fill=Adjusted.P.value))+
  geom_bar(position="stack", stat="identity")+
  labs(title=paste0(folder,"_","DrugMatrix_Gene_Targets_Comparison"))+
  labs(x="Module names")+
  theme(axis.text.x=element_text(angle=90,hjust=1)) +
  labs(y="Number of genes overlap")+
  labs(caption="based on data from enrichR")+
  scale_fill_gradient(low="black",high="red")
  #theme(plot.margin = margin(2,2,2,2, "cm"), plot.background = element_rect(fill = "white"))
print(p18)
dev.off()
```

###########################################################################################DSigDB base analysis############################################################################################################

###Step36: DSigDB target genes analysis results

```{r}
#Export DSigDB pathway result
my_genes_DSigDB<-as.data.frame(enriched[["DSigDB"]])
my_genes_DSigDB_sig0.05<-my_genes_DSigDB[my_genes_DSigDB$Adjusted.P.value <0.05,]
head(my_genes_DSigDB_sig0.05)
head(my_genes_DSigDB)
```

```{r}
#Creating a new column with number of genes that overlapped
my_genes_DSigDB_sig0.05_new<-my_genes_DSigDB_sig0.05

my_genes_DSigDB_sig0.05_new$Overlap_Number<-my_genes_DSigDB_sig0.05$Overlap

my_genes_DSigDB_sig0.05_new$Overlap_Number<-gsub("/.*","",my_genes_DSigDB_sig0.05_new$Overlap_Number)

my_genes_DSigDB_sig0.05_new$Overlap_Number<-as.integer(my_genes_DSigDB_sig0.05_new$Overlap_Number)

write.csv(my_genes_DSigDB_sig0.05_new,file="Step36_result_DSigDB_sig0.05_TAPbyQNP.csv")
```

```{r}
# Basic barplot
folder=getwd()
pdf(paste0("Step36_plot_sig0.05-DSigDB_Pathway_plot_", "TAPbyQNP",".pdf"), height=10, width=5)
p19<-ggplot(data=my_genes_DSigDB_sig0.05_new, aes(x=Term, y=Overlap_Number, fill=Adjusted.P.value))+
  geom_bar(position="stack", stat="identity")+
  labs(title=paste0(folder,"_","DSigDB_Gene_Targets_Comparison"))+
  labs(x="Module names")+
  theme(axis.text.x=element_text(angle=90,hjust=1)) +
  labs(y="Number of genes overlap")+
  labs(caption="based on data from enrichR")+
  scale_fill_gradient(low="black",high="red")
  #theme(plot.margin = margin(2,2,2,2, "cm"), plot.background = element_rect(fill = "white"))
print(p19)
dev.off()
```

```{r}
#Creating a new column with number of genes that overlapped
my_genes_DSigDB_new<-my_genes_DSigDB

my_genes_DSigDB_new$Overlap_Number<-my_genes_DSigDB$Overlap

my_genes_DSigDB_new$Overlap_Number<-gsub("/.*","",my_genes_DSigDB_new$Overlap_Number)

my_genes_DSigDB_new$Overlap_Number<-as.integer(my_genes_DSigDB_new$Overlap_Number)

write.csv(my_genes_DSigDB_new,file="Step36_result_DSigDB_TAPbyQNP.csv")
```

```{r}
# Basic barplot
folder=getwd()
pdf(paste0("Step36_plot_DSigDB_Pathway_plot_", "TAPbyQNP",".pdf"), height=10, width=5)
p20<-ggplot(data=my_genes_DSigDB_new, aes(x=Term, y=Overlap_Number, fill=Adjusted.P.value))+
  geom_bar(position="stack", stat="identity")+
  labs(title=paste0(folder,"_","DSigDB_Gene_Targets_Comparison"))+
  labs(x="Module names")+
  theme(axis.text.x=element_text(angle=90,hjust=1)) +
  labs(y="Number of genes overlap")+
  labs(caption="based on data from enrichR")+
  scale_fill_gradient(low="black",high="red")
  #theme(plot.margin = margin(2,2,2,2, "cm"), plot.background = element_rect(fill = "white"))
print(p20)
dev.off()
```

###########################################################################################Epigenomics_Roadmap_HM_ChIP-seq base analysis############################################################################################################

###Step37: Epigenomics_Roadmap_HM_ChIP-seq target genes analysis results

```{r}
#Export Epigenomics_Roadmap_HM_ChIP-seq pathway result
my_genes_Epigenomics_Roadmap_HM_ChIPseq<-as.data.frame(enriched[["Epigenomics_Roadmap_HM_ChIP-seq"]])
my_genes_Epigenomics_Roadmap_HM_ChIPseq_sig0.05<-my_genes_Epigenomics_Roadmap_HM_ChIPseq[my_genes_Epigenomics_Roadmap_HM_ChIPseq$Adjusted.P.value <0.05,]
head(my_genes_Epigenomics_Roadmap_HM_ChIPseq_sig0.05)
head(my_genes_Epigenomics_Roadmap_HM_ChIPseq)
```

```{r}
#Creating a new column with number of genes that overlapped
my_genes_Epigenomics_Roadmap_HM_ChIPseq_sig0.05_new<-my_genes_Epigenomics_Roadmap_HM_ChIPseq_sig0.05

my_genes_Epigenomics_Roadmap_HM_ChIPseq_sig0.05_new$Overlap_Number<-my_genes_Epigenomics_Roadmap_HM_ChIPseq_sig0.05$Overlap

my_genes_Epigenomics_Roadmap_HM_ChIPseq_sig0.05_new$Overlap_Number<-gsub("/.*","",my_genes_Epigenomics_Roadmap_HM_ChIPseq_sig0.05_new$Overlap_Number)

my_genes_Epigenomics_Roadmap_HM_ChIPseq_sig0.05_new$Overlap_Number<-as.integer(my_genes_Epigenomics_Roadmap_HM_ChIPseq_sig0.05_new$Overlap_Number)

write.csv(my_genes_Epigenomics_Roadmap_HM_ChIPseq_sig0.05_new,file="Step37_result_Epigenomics_Roadmap_HM_ChIP-seq_sig0.05_TAPbyQNP.csv")
```

```{r}
# Basic barplot
folder=getwd()
pdf(paste0("Step37_plot_sig0.05-Epigenomics_Roadmap_HM_ChIP-seq_Pathway_plot_", "TAPbyQNP",".pdf"), height=10, width=5)
p19<-ggplot(data=my_genes_Epigenomics_Roadmap_HM_ChIPseq_sig0.05_new, aes(x=Term, y=Overlap_Number, fill=Adjusted.P.value))+
  geom_bar(position="stack", stat="identity")+
  labs(title=paste0(folder,"_","Epigenomics_Roadmap_HM_ChIP-seq_Gene_Targets_Comparison"))+
  labs(x="Module names")+
  theme(axis.text.x=element_text(angle=90,hjust=1)) +
  labs(y="Number of genes overlap")+
  labs(caption="based on data from enrichR")+
  scale_fill_gradient(low="black",high="red")
  #theme(plot.margin = margin(2,2,2,2, "cm"), plot.background = element_rect(fill = "white"))
print(p19)
dev.off()
```

```{r}
#Creating a new column with number of genes that overlapped
my_genes_Epigenomics_Roadmap_HM_ChIPseq_new<-my_genes_Epigenomics_Roadmap_HM_ChIPseq

my_genes_Epigenomics_Roadmap_HM_ChIPseq_new$Overlap_Number<-my_genes_Epigenomics_Roadmap_HM_ChIPseq$Overlap

my_genes_Epigenomics_Roadmap_HM_ChIPseq_new$Overlap_Number<-gsub("/.*","",my_genes_Epigenomics_Roadmap_HM_ChIPseq_new$Overlap_Number)

my_genes_Epigenomics_Roadmap_HM_ChIPseq_new$Overlap_Number<-as.integer(my_genes_Epigenomics_Roadmap_HM_ChIPseq_new$Overlap_Number)

write.csv(my_genes_Epigenomics_Roadmap_HM_ChIPseq_new,file="Step37_result_Epigenomics_Roadmap_HM_ChIP-seq_TAPbyQNP.csv")
```

```{r}
# Basic barplot
folder=getwd()
pdf(paste0("Step37_plot_Epigenomics_Roadmap_HM_ChIP-seq_Pathway_plot_", "TAPbyQNP",".pdf"), height=10, width=5)
p20<-ggplot(data=my_genes_Epigenomics_Roadmap_HM_ChIPseq_new, aes(x=Term, y=Overlap_Number, fill=Adjusted.P.value))+
  geom_bar(position="stack", stat="identity")+
  labs(title=paste0(folder,"_","Epigenomics_Roadmap_HM_ChIP-seq_Gene_Targets_Comparison"))+
  labs(x="Module names")+
  theme(axis.text.x=element_text(angle=90,hjust=1)) +
  labs(y="Number of genes overlap")+
  labs(caption="based on data from enrichR")+
  scale_fill_gradient(low="black",high="red")
  #theme(plot.margin = margin(2,2,2,2, "cm"), plot.background = element_rect(fill = "white"))
print(p20)
dev.off()
```

###########################################################################################ENCODE_and_ChEA_Consensus_TFs_from_ChIP-X base analysis############################################################################################################

###Step38: ENCODE_and_ChEA_Consensus_TFs_from_ChIP-X target genes analysis results

```{r}
#Export ENCODE_and_ChEA_Consensus_TFs_from_ChIP-X pathway result
my_genes_ENCODE_and_ChEA_Consensus_TFs_from_ChIPX<-as.data.frame(enriched[["ENCODE_and_ChEA_Consensus_TFs_from_ChIP-X"]])
my_genes_ENCODE_and_ChEA_Consensus_TFs_from_ChIPX_sig0.05<-my_genes_ENCODE_and_ChEA_Consensus_TFs_from_ChIPX[my_genes_ENCODE_and_ChEA_Consensus_TFs_from_ChIPX$Adjusted.P.value <0.05,]
head(my_genes_ENCODE_and_ChEA_Consensus_TFs_from_ChIPX_sig0.05)
head(my_genes_ENCODE_and_ChEA_Consensus_TFs_from_ChIPX)
```

```{r}
#Creating a new column with number of genes that overlapped
my_genes_ENCODE_and_ChEA_Consensus_TFs_from_ChIPX_sig0.05_new<-my_genes_ENCODE_and_ChEA_Consensus_TFs_from_ChIPX_sig0.05

my_genes_ENCODE_and_ChEA_Consensus_TFs_from_ChIPX_sig0.05_new$Overlap_Number<-my_genes_ENCODE_and_ChEA_Consensus_TFs_from_ChIPX_sig0.05$Overlap

my_genes_ENCODE_and_ChEA_Consensus_TFs_from_ChIPX_sig0.05_new$Overlap_Number<-gsub("/.*","",my_genes_ENCODE_and_ChEA_Consensus_TFs_from_ChIPX_sig0.05_new$Overlap_Number)

my_genes_ENCODE_and_ChEA_Consensus_TFs_from_ChIPX_sig0.05_new$Overlap_Number<-as.integer(my_genes_ENCODE_and_ChEA_Consensus_TFs_from_ChIPX_sig0.05_new$Overlap_Number)

write.csv(my_genes_ENCODE_and_ChEA_Consensus_TFs_from_ChIPX_sig0.05_new,file="Step38_result_ENCODE_and_ChEA_Consensus_TFs_from_ChIP-X_sig0.05_TAPbyQNP.csv")
```

```{r}
# Basic barplot
folder=getwd()
pdf(paste0("Step38_plot_sig0.05-ENCODE_and_ChEA_Consensus_TFs_from_ChIP-X_Pathway_plot_", "TAPbyQNP",".pdf"), height=10, width=5)
p19<-ggplot(data=my_genes_ENCODE_and_ChEA_Consensus_TFs_from_ChIPX_sig0.05_new, aes(x=Term, y=Overlap_Number, fill=Adjusted.P.value))+
  geom_bar(position="stack", stat="identity")+
  labs(title=paste0(folder,"_","ENCODE_and_ChEA_Consensus_TFs_from_ChIP-X_Gene_Targets_Comparison"))+
  labs(x="Module names")+
  theme(axis.text.x=element_text(angle=90,hjust=1)) +
  labs(y="Number of genes overlap")+
  labs(caption="based on data from enrichR")+
  scale_fill_gradient(low="black",high="red")
  #theme(plot.margin = margin(2,2,2,2, "cm"), plot.background = element_rect(fill = "white"))
print(p19)
dev.off()
```

```{r}
#Creating a new column with number of genes that overlapped
my_genes_ENCODE_and_ChEA_Consensus_TFs_from_ChIPX_new<-my_genes_ENCODE_and_ChEA_Consensus_TFs_from_ChIPX

my_genes_ENCODE_and_ChEA_Consensus_TFs_from_ChIPX_new$Overlap_Number<-my_genes_ENCODE_and_ChEA_Consensus_TFs_from_ChIPX$Overlap

my_genes_ENCODE_and_ChEA_Consensus_TFs_from_ChIPX_new$Overlap_Number<-gsub("/.*","",my_genes_ENCODE_and_ChEA_Consensus_TFs_from_ChIPX_new$Overlap_Number)

my_genes_ENCODE_and_ChEA_Consensus_TFs_from_ChIPX_new$Overlap_Number<-as.integer(my_genes_ENCODE_and_ChEA_Consensus_TFs_from_ChIPX_new$Overlap_Number)

write.csv(my_genes_ENCODE_and_ChEA_Consensus_TFs_from_ChIPX_new,file="Step38_result_ENCODE_and_ChEA_Consensus_TFs_from_ChIP-X_TAPbyQNP.csv")
```

```{r}
# Basic barplot
folder=getwd()
pdf(paste0("Step38_plot_ENCODE_and_ChEA_Consensus_TFs_from_ChIP-X_Pathway_plot_", "TAPbyQNP",".pdf"), height=10, width=5)
p20<-ggplot(data=my_genes_ENCODE_and_ChEA_Consensus_TFs_from_ChIPX_new, aes(x=Term, y=Overlap_Number, fill=Adjusted.P.value))+
  geom_bar(position="stack", stat="identity")+
  labs(title=paste0(folder,"_","ENCODE_and_ChEA_Consensus_TFs_from_ChIP-X_Gene_Targets_Comparison"))+
  labs(x="Module names")+
  theme(axis.text.x=element_text(angle=90,hjust=1)) +
  labs(y="Number of genes overlap")+
  labs(caption="based on data from enrichR")+
  scale_fill_gradient(low="black",high="red")
  #theme(plot.margin = margin(2,2,2,2, "cm"), plot.background = element_rect(fill = "white"))
print(p20)
dev.off()
```

###Step39: Organization and saving session (software version) information 

```{r}
sessionInfo()
toLatex(sessionInfo())
```

```{r}
#save image
save.image(file="TAPbyQNPEnrichR.RData")
```

```{r}
#Organize of files
library(filesstrings)

dir.create("TAPbyQNPEnrichR")
file.move(list.files(pattern = "*TAPbyQNP.pdf"), "TAPbyQNPEnrichR")
file.move(list.files(pattern = "*TAPbyQNP.csv"), "TAPbyQNPEnrichR", overwrite = TRUE)
file.move(list.files(pattern = "TAPbyQNPEnrichR.RData"), "TAPbyQNPEnrichR")
```

```{r}
#Remove .RData and clear environment to free up memory
rm(list=ls())
file.remove("temp.RData")
gc()
```

###########################################################################################<Start next pipeline>############################################################################################################










