---
title: "script6_alternative_corr_spearman"
author: "Shradha Mukherjee"
date: "April 16, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###############################################Different correlations############################################################################
####################################HuAgeGBsplit#######################################
###Step13: Load libraries, set working directory and Import data for WGCNA###
```{r}
#If restarting program uncomment line below
#load(file="temp.RData")
#load("./Module_Trait_wgcnaRData/WGCNA_temp75.RData")
load("./Module_Trait_wgcnaRData/WGCNA_truncated75.RData")
#save working directory location
wd<-getwd()
wd
``` 

```{r}
#Load additional functions required for this pipeline
#Reference: Miller, J.A., Horvath, S., and Geschwind, D.H. (2010). Divergence of Human and mouse brain transcriptome highlights Alzheimer disease pathways. Proceedings of the National Academy of Sciences of the United States of America 107, 12698-12703.

write.geneList <- function(PG, filename, allProbes=0, allGenes=0, probe="g")
{
## These functions write a genelist / probelist to a file of geneNames

## USER inputs
# PG = the probe/gene you want written to a gene list
# allProbes = the list of probe names for the above probes
# allGenes = the list of gene names for the corresponding probes
# filename = the filename (can include folder)
# probe = the default ("g") says PG is a gene and doesn''t need to be converted
#         to a gene.  Otherwise PG is assumed to be a probe and converted

gene = PG
if (probe!="g") {
  gene = probe2Gene(PG,allProbes,allGenes)
}
write(gene,filename,sep="\n")

}

cor.test.l = function(x){
## Performs a Pearson correlation on a vector of genes
 ct = cor.test(x,var)
 return(c(ct$est,ct$p.val))
}
```

```{r}
#library(BiocInstaller)
#biocLite("qvalue")
#install.packages(c("impute","dynamicTreeCut","flashClust","Hmisc","WGCNA","stringi","enrichR","filesstrings"))
library(impute)
library(dynamicTreeCut)
library(qvalue)
library(flashClust)
library(Hmisc)
library(WGCNA)
library(stringi)
library(stringr)
library(enrichR)#for pathway analysis
library(filesstrings)#for file organization
options(stringsAsFactors = FALSE)
```

###Step19: Visualization of trait module relatonships for data A1###
#In this step we use the coded metadata files

#Relating modules to physiological traits for A1
```{r}
# For data A1
# Define numbers of genes and samples
nGenesA1 = nrow(datExprA1g2)
nSamplesA1 = ncol(datExprA1g2)
# Recalculate MEs with color labels
MEs0A1= moduleEigengenes(t(datExprA1g2),modulesA1)$eigengenes
MEsA1= orderMEs(MEs0A1)
#modTraitCorA1 = cor(MEsA1, metadataA1g_coded, use = "p")
#modTraitCorA1 = cor(MEsA1, metadataA1g_coded, use="complete.obs", method = c("pearson", "kendall", "spearman"))
modTraitCorA1 = cor(MEsA1, metadataA1g_coded, use="pairwise.complete.obs", method = c("spearman"))

modTraitPA1 = corPvalueStudent(modTraitCorA1, nSamplesA1)
textMatrixA1 = paste(signif(modTraitCorA1, 2), "\n(",
signif(modTraitPA1, 1), ")", sep = "")
dim(textMatrixA1) = dim(modTraitCorA1)
par(mar = c(6, 8.5, 3, 3))
# Display the correlation values within a heatmap plot
labeledHeatmap(Matrix = modTraitCorA1, xLabels = names(metadataA1g_coded),
yLabels = names(MEsA1), ySymbols = names(MEsA1), cex.lab = 0.05,
colorLabels =FALSE,colors=greenWhiteRed(50),textMatrix=textMatrixA1,
setStdMargins = FALSE, cex.text = 0.05, zlim = c(-1,1),
main = paste("A1_Module-trait relationships colors"))
dev.print(pdf,"Step19_plot_A1_relating modules to trait colors spearman.pdf", width=5, height=8)

#This is for color module trait table
colnames(modTraitPA1) = paste("p.value.", colnames(modTraitCorA1), sep="");
out3<-cbind(Module=rownames(modTraitCorA1), modTraitCorA1, modTraitPA1)
dim(out3)
write.table(out3, "Step19_result_A1_relating modules to trait colors spearman.csv", sep=",",row.names=F)
```

#Same as above for labeled modules
#Relating modules to physiological traits for A1
```{r}
# For data A1
# Define numbers of genes and samples
nGenesA1L = nrow(datExprA1g2)
nSamplesA1L = ncol(datExprA1g2)
# Recalculate MEs with color labels
MEs0A1L= moduleEigengenes(t(datExprA1g2),modulesA1L)$eigengenes
MEsA1L= orderMEs(MEs0A1L)
#modTraitCorA1L = cor(MEsA1L, metadataA1g_coded, use = "p")
#modTraitCorA1L = cor(MEsA1L, metadataA1g_coded, use="complete.obs", method = c("pearson", "kendall", "spearman"))
modTraitCorA1L = cor(MEsA1L, metadataA1g_coded, use="pairwise.complete.obs", method = c("spearman"))
modTraitPA1L = corPvalueStudent(modTraitCorA1L, nSamplesA1L)
textMatrixA1L = paste(signif(modTraitCorA1L, 2), "\n(",
signif(modTraitPA1L, 1), ")", sep = "")
dim(textMatrixA1L) = dim(modTraitCorA1L)
par(mar = c(6, 8.5, 3, 3))
# Display the correlation values within a heatmap plot
labeledHeatmap(Matrix = modTraitCorA1L, xLabels = names(metadataA1g_coded),
yLabels = names(MEsA1L), ySymbols = names(MEsA1L), cex.lab = 0.25,
colorLabels =FALSE,colors=greenWhiteRed(50),textMatrix=textMatrixA1L,
setStdMargins = FALSE, cex.text = 0.25, zlim = c(-1,1),
main = paste("A1_Module-trait relationships labels"))
dev.print(pdf,"Step19_plot_A1_relating modules to trait labels spearman.pdf", width=5, height=8)

#This is for label module trait table
colnames(modTraitPA1L) = paste("p.value.", colnames(modTraitCorA1L), sep="");
out3L<-cbind(Module=rownames(modTraitCorA1L), modTraitCorA1L, modTraitPA1L)
dim(out3L)
write.table(out3L, "Step19_result_A1_relating modules to trait labels spearman.csv", sep=",",row.names=F)
```

```{r}
#Gene trait significance and correlation for entire gene set i.e. all genes from all modules
#geneTraitCorA1 = cor(t(datExprA1g2), metadataA1g_coded, use = "p")
geneTraitCorA1 = cor(t(datExprA1g2), metadataA1g_coded, use="pairwise.complete.obs", method = c("spearman"))
geneTraitPA1 = corPvalueStudent(geneTraitCorA1, nSamplesA1)
#This is for color gene trait table
colnames(geneTraitPA1) = paste("p.value.", colnames(geneTraitCorA1), sep="");
out3gene<-cbind(GeneName=rownames(geneTraitCorA1), geneTraitCorA1, geneTraitPA1)
dim(out3gene)
write.table(out3gene, "Step19_result_A1_relating all genes to traits spearman.csv", sep=",",row.names=F)
```

#Same as above for labeled modules but only significant ones for Grade4 after revieweing results from above csv of all modules
#Relating modules to physiological traits for A1
```{r}
# For data A1
# Define numbers of genes and samples
nGenesA1L = nrow(datExprA1g2)
nSamplesA1L = ncol(datExprA1g2)
# Recalculate MEs with color labels
MEs0A1L= moduleEigengenes(t(datExprA1g2),modulesA1L)$eigengenes
MEsA1L= orderMEs(MEs0A1L)

#modification to subset significant modules only
MEsA1Lnew=MEsA1L[,c("MEHuAgeGBsplit_36","MEHuAgeGBsplit_35","MEHuAgeGBsplit_33","MEHuAgeGBsplit_27","MEHuAgeGBsplit_26","MEHuAgeGBsplit_24","MEHuAgeGBsplit_18","MEHuAgeGBsplit_16","MEHuAgeGBsplit_08","MEHuAgeGBsplit_00")]
#modification to subset traits of interest only
metadataA1g_coded_new=metadataA1g_coded[,c("DiseaseGrade_2", "DiseaseGrade_3", "DiseaseGrade_4")]

#modTraitCorA1L = cor(MEsA1Lnew, metadataA1g_coded, use = "p")
#modTraitCorA1L = cor(MEsA1Lnew, metadataA1g_coded, use="complete.obs", method = c("pearson", "kendall", "spearman"))
modTraitCorA1L = cor(MEsA1Lnew, metadataA1g_coded_new, use="pairwise.complete.obs", method = c("spearman"))
modTraitPA1L = corPvalueStudent(modTraitCorA1L, nSamplesA1L)
textMatrixA1L = paste(signif(modTraitCorA1L, 2), "\n(",
signif(modTraitPA1L, 1), ")", sep = "")
dim(textMatrixA1L) = dim(modTraitCorA1L)
par(mar = c(6, 8.5, 3, 3))
# Display the correlation values within a heatmap plot
labeledHeatmap(Matrix = modTraitCorA1L, xLabels = names(metadataA1g_coded_new),
yLabels = names(MEsA1Lnew), ySymbols = names(MEsA1Lnew), cex.lab = 1.0,
colorLabels =FALSE,colors=greenWhiteRed(50),textMatrix=textMatrixA1L,
setStdMargins = FALSE, cex.text = 1.0, zlim = c(-1,1),
main = paste("A1_Module-trait relationships labels"))
dev.print(pdf,"Step19_plot_A1_relating modules to trait labels spearman_significant.pdf", width=5, height=8)

#This is for label module trait table
colnames(modTraitPA1L) = paste("p.value.", colnames(modTraitCorA1L), sep="");
out3L<-cbind(Module=rownames(modTraitCorA1L), modTraitCorA1L, modTraitPA1L)
dim(out3L)
write.table(out3L, "Step19_result_A1_relating modules to trait labels spearman_significant.csv", sep=",",row.names=F)
```

###Step21: merging trait association results and cell type enrichment results###
```{r}
corr_pearson=read.csv("./Module_Trait_wgcnaRData/Step19_result_A1_relating modules to trait colors.csv", header=T, sep=',')
colnames(corr_pearson)
DT::datatable(corr_pearson[1:3,])
```

```{r}
#remove the character ME at the start of the module name
corr_pearson$Module<-sub('.', '', corr_pearson$Module)
corr_pearson$Module<-sub('.', '', corr_pearson$Module)
DT::datatable(corr_pearson[1:3,])
```

```{r}
corr_spearman=read.csv("./Module_Trait_wgcnaRData/Step19_result_A1_relating modules to trait colors spearman.csv", header=T, sep=',')
colnames(corr_spearman)
DT::datatable(corr_spearman[1:3,])
```

```{r}
#remove the character ME at the start of the module name
corr_spearman$Module<-sub('.', '', corr_spearman$Module)
corr_spearman$Module<-sub('.', '', corr_spearman$Module)
DT::datatable(corr_spearman[1:3,])
```

```{r}
modules_celltypes=read.csv("./enrichmentsCellTypeFullHuman_OvGenes/enrichmentsCellTypeFullHuman_Sigificantcolors.csv", header=T, sep=',') 
colnames(modules_celltypes)
DT::datatable(modules_celltypes)
```

```{r}
modules_celltypes_corr_pearson=merge(modules_celltypes,corr_pearson, by.x = "InputCategories", by.y = "Module", all = FALSE)
write.csv(modules_celltypes_corr_pearson,"Step21_result_modules_celltypes_corr_pearson.csv")
DT::datatable(head(modules_celltypes_corr_pearson))
```

```{r}
modules_celltypes_corr_spearman=merge(modules_celltypes,corr_spearman, by.x = "InputCategories", by.y = "Module", all = FALSE)
write.csv(modules_celltypes_corr_spearman,"Step21_result_modules_celltypes_corr_spearman.csv")
DT::datatable(head(modules_celltypes_corr_spearman))
```

###Step21: merging trait association results and cell type enrichment results###
#Same as above but with labels
```{r}
corr_pearsonL=read.csv("./Module_Trait_wgcnaRData/Step19_result_A1_relating modules to trait labels.csv", header=T, sep=',')
colnames(corr_pearsonL)
DT::datatable(corr_pearsonL[1:3,])
```

```{r}
#remove the character ME at the start of the module name
corr_pearsonL$Module<-sub('.', '', corr_pearsonL$Module)
corr_pearsonL$Module<-sub('.', '', corr_pearsonL$Module)
DT::datatable(corr_pearsonL[1:3,])
```

```{r}
corr_spearmanL=read.csv("./Module_Trait_wgcnaRData/Step19_result_A1_relating modules to trait labels spearman.csv", header=T, sep=',')
colnames(corr_spearmanL)
DT::datatable(corr_spearmanL[1:3,])
```

```{r}
#remove the character ME at the start of the module name
corr_spearmanL$Module<-sub('.', '', corr_spearmanL$Module)
corr_spearmanL$Module<-sub('.', '', corr_spearmanL$Module)
DT::datatable(corr_spearmanL[1:3,])
```

```{r}
modules_celltypesL=read.csv("./enrichmentsCellTypeFullHuman_OvGenes/enrichmentsCellTypeFullHuman_Sigificantlabels.csv", header=T, sep=',') 
colnames(modules_celltypesL)
DT::datatable(modules_celltypesL)
```

```{r}
modules_celltypesL_corr_pearsonL=merge(modules_celltypesL,corr_pearsonL, by.x = "InputCategories", by.y = "Module", all = FALSE)
write.csv(modules_celltypesL_corr_pearsonL,"Step21_result_modules_celltypesL_corr_pearsonL.csv")
DT::datatable(head(modules_celltypesL_corr_pearsonL))
```

```{r}
modules_celltypesL_corr_spearmanL=merge(modules_celltypesL,corr_spearmanL, by.x = "InputCategories", by.y = "Module", all = FALSE)
write.csv(modules_celltypesL_corr_spearmanL,"Step21_result_modules_celltypesL_corr_spearmanL.csv")
DT::datatable(head(modules_celltypesL_corr_spearmanL))
```

```{r}
save.image(file="CorrCellType.RData")
#rm(list=ls())
#gc()
#To reload uncomment code below
#load(file="temp.RData")
```

#Step22: Organization and saving session (software version) information 
```{r}
sessionInfo()
toLatex(sessionInfo())
```

```{r}
#Organize of files
#library(filesstrings)

dir.create("Module_Trait_wgcnaRData")
file.move(list.files(pattern = 'Step19_result_A1_relating*'), "Module_Trait_wgcnaRData")
file.move(list.files(pattern = 'Step19_plot_A1_relating*'), "Module_Trait_wgcnaRData")
file.move(list.files(pattern = 'Step21_result*'), "Module_Trait_wgcnaRData")
file.move(list.files(pattern = 'CorrCellType.RData'), "Module_Trait_wgcnaRData")
```

```{r}
#Remove .RData and clear environment to free up memory
rm(list=ls())
file.remove("temp.RData")
gc()
```
